### 2019-03-29 IEEE_TC_submission.d/preliminaries.tex
ssr

We present some definitions and recall
a known result regarding NCFs which allow us
to define a normalized representation for NCFs.
This representation plays an important role in several
problems considered in later sections.
We also show that, in general, the symmetry level
of a Boolean function cannot be efficiently approximated to within any
factor $\rho \geq 1$, unless \textbf{P} = \cnp.

@@

Recall that any NCF $f$ with $n$ variables,
denoted by $x_1$, $x_2$, $\ldots$, $x_n$,~
is specified using a variable ordering 
$x_{\pi(1)}$, $x_{\pi(2)}$, $\ldots$,  $x_{\pi(n)}$,
where $\pi$ is a permutation of $\{1, 2, \ldots, n\}$.
%% We will refer to this as the \textbf{lexicographic} ordering
%% of the variables in the specification.
Throughout this paper, we will assume without loss of generality
that the variable ordering uses the identity permutation 
so that $x_i$ is the variable tested in line $i$, $1 \leq i \leq n$. 
We assume that an NCF $f$ with $n$
variables is specified using the simplified representation with $n$ lines. 
Unless otherwise mentioned, the ``Default" line (which is assigned the number $n+1$)
in the simplified representation of an NCF is \emph{not} considered
in the results stated in this section.
We will use the following result from \cite{Stearns-etal-2018}.

@@

\medskip
From Part~1 of Observation~\ref{obs:ncf_transformations},
it follows that the lines within the same layer of an NCF
representation can be permuted without changing the function.
Part~2 of Observation~\ref{obs:ncf_transformations} points
out that for any NCF $f$ with $n \geq 2$ variables, there is a simplified 
representation in which lines $n-1$ and $n$ are in the same layer.

%% It can be verified that the number of layers in the 
%% extended monomial formula for a NCF (as defined in \cite{Li-etal-2013})
%% is the same as the number of layers in the normalized representation.

\medskip
We can now define the notion of a \textbf{default-normalized} 
representation for NCFs.

>>>>

We present some definitions and recall
a known result regarding NCFs which allow us
to define a normalized representation for NCFs.
This representation plays an important role in several
problems considered in later sections.
We also show (Theorem~\ref{thm:approx_sym_level_hard}) 
that, in general, the symmetry level
of a Boolean function cannot be efficiently approximated to within any
factor $\rho \geq 1$, unless \textbf{P} = \cnp.

@@

Recall that any NCF $f$ with $n$ variables,
denoted by $x_1$, $x_2$, $\ldots$, $x_n$,~
is specified using a variable ordering 
$x_{\pi(1)}$, $x_{\pi(2)}$, $\ldots$,  $x_{\pi(n)}$,
where $\pi$ is a permutation of $\{1, 2, \ldots, n\}$.
Throughout this paper, we will assume without loss of generality
that the variable ordering uses the identity permutation 
so that $x_i$ is the variable tested in line $i$, $1 \leq i \leq n$. 
We assume that an NCF $f$ with $n$
variables is specified using the simplified representation with $n$ lines. 
Unless otherwise mentioned, the ``Default" line (which is assigned the number $n+1$)
in the simplified representation of an NCF is \emph{not} considered
in the results stated in this section.
We will use the following result from \cite{Stearns-etal-2018}.

@@

\medskip
From Part~1 of Observation~\ref{obs:ncf_transformations},
it follows that the lines within the same layer of an NCF
representation can be permuted without changing the function.
Part~2 of Observation~\ref{obs:ncf_transformations} points
out that for any NCF $f$ with $n \geq 2$ variables, there is a simplified 
representation in which lines $n-1$ and $n$ are in the same layer.
We can now define the notion of a \textbf{default-normalized} 
representation for NCFs.
